New_Data_Coherence

### 2019-09-23 Analysis/Coherence_Calculations_New.Rmd
adapt to new style

#Adding p-values from permutation test
#Biogrid
biogrid_p = bind_rows(readRDS("./data/Permutation_Results/biogrid_p_1k.rds") %>% as.data.frame(.), readRDS("./data/Permutation_Results/biogrid_p_psych_1k.rds") %>% as.data.frame(.))

#String
string_p = bind_rows(readRDS("./data/Permutation_Results/string_p_1k.rds") %>% as.data.frame(.), readRDS("./data/Permutation_Results/string_p_psych_1k.rds") %>% as.data.frame(.), readRDS("./data/Permutation_Results/string_p_neuro_1k.rds") %>% as.data.frame(.))

#String Filtered
string_filt_p = bind_rows(readRDS("./data/Permutation_Results/string_filt_p_1k.rds") %>% as.data.frame(.), readRDS("./data/Permutation_Results/string_filt_p_psych_1k.rds") %>% as.data.frame(.), readRDS("./data/Permutation_Results/string_filt_p_neuro_1k.rds") %>% as.data.frame(.))

>>>>

#Adding p-values from permutation test
#Biogrid
biogrid_p = readRDS("./data/Permutation_Results/biogrid_p_1k.rds") %>% as.data.frame(.) %>% dplyr::select(-new_coherence)

#String
string_p = readRDS("./data/Permutation_Results/string_p_1k.rds") %>% as.data.frame(.)  %>% dplyr::select(-new_coherence)

#String Filtered
string_filt_p = readRDS("./data/Permutation_Results/string_filt_p_1k.rds") %>% as.data.frame(.)  %>% dplyr::select(-new_coherence)
